Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-11-30 paper-ApJ/ms.tex
Cite Fraser-Mackelvie 2020

>>>>

\citet{2020MNRAS.495.4158F} find that quenched galaxies tend to host longer bars
than star-forming galaxies. This provides some support for our proposed
mechanism since there is evidence quenching can occur through gas depletion
\citep[e.g.][]{2021Natur.597..485W}. However, this correlation could be
explained simply by the fact that longer bars ought to be more efficient at
quenching their host galaxies \citep[e.g][]{2015AA...580A.116G}.
